### 2023-05-25 application.tex
up

Without loss of generality hence let us consider only the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
$$\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).$$
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear \cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

@@

\begin{proof}
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^d$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \alain{à faire}	
%		Recall that reachability is NP-complete for integer VASS. 
\end{proof}

>>>>

Without loss of generality hence let us consider only the case when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
$$\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).$$
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear~\cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}

@@

\begin{proof}
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^d$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \alain{à faire}	
%		Recall that reachability is NP-complete for integer VASS. 
\mathieu{Comparé à la preuve précédente, il faut vérifier que le Home space problem est décidable dans les $\mathbb{Z}$-VASS}
\mathieu{Proposition 2, Proposition 3 dans [9] valent aussi bien pour les VASS que les 
 $\mathbb{Z}$-VASS à mon sens}
 \mathieu{Pour le Lemma 4, par contre, c'est peut-être moins évident. DC (can decrease the token) et NDC (cannot decrease the token) sont plus difficile à calculer (par exemple, MIN(DC) n'est pas calculable).}
\end{proof}
